IMPC Mouse data - Variance in sex differences

### 2019-11-21 scripts/2019_Nov1-FiguresRearranged_IMPC_variance_and_sex_difference.Rmd
Restyle using styler and use `here` package for rubst loading

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      warning = FALSE,
                      message = FALSE,
                      cache = TRUE,
                      tidy = TRUE)

@@

```{r, include=FALSE}
getwd()
```

@@

```{r}
library(readr)
library(dplyr)
library(metafor)
library(devtools)
library(purrr)
library(tidyverse)
library(tibble)
library(kableExtra)
library(robumeta)
library(ggpubr)
library(ggplot2)
```

### Loading functions 
#### Functions for preparing the data for meta analyses
1) "Population statistics"
```{r}
calculate_population_stats <- function(mydata, min_individuals = 5) {
  mydata %>% 
    group_by(population, strain_name, production_center, sex) %>% 
    summarise(
      trait = parameter_name[1],
      x_bar = mean(data_point),
      x_sd = sd(data_point),
      n_ind = n()
    ) %>% 
    ungroup() %>%
    filter(n_ind > min_individuals) %>% 
    # Check both sexes present & filter those missing
    group_by(population) %>% 
    mutate(
      n_sex = n_distinct(sex)
    ) %>% 
    ungroup() %>%
    filter(n_sex ==2) %>% 
    select(-n_sex) %>%
    arrange(production_center, strain_name, population, sex)
}
```

@@

  mydata[i,] %>% 
  select(strain_name, production_center, trait) %>%
    mutate(
      effect_size_CVR = Calc.lnCVR(CMean = input$x1i, CSD = input$sd1i, CN = input$n1i, EMean = input$x2i, ESD = input$sd2i, EN = input$n2i),
      sample_variance_CVR = Calc.var.lnCVR(CMean = input$x1i, CSD = input$sd1i, CN = input$n1i, EMean = input$x2i, ESD = input$sd2i, EN = input$n2i),
      effect_size_VR = Calc.lnVR(CSD = input$sd1i, CN = input$n1i, ESD = input$sd2i, EN = input$n2i),
      sample_variance_VR = Calc.var.lnVR(CN = input$n1i, EN = input$n2i),
      effect_size_RR = Calc.lnRR(CMean = input$x1i, CSD = input$sd1i, CN = input$n1i, EMean = input$x2i, ESD = input$sd2i, EN = input$n2i),
      sample_variance_RR = Calc.var.lnRR(CMean = input$x1i, CSD = input$sd1i, CN = input$n1i, EMean = input$x2i, ESD = input$sd2i, EN = input$n2i),
      err = as.factor(seq_len(n()))
    )

}
```

@@

Calc.lnCVR <- function(CMean, CSD, CN, EMean, ESD, EN){
  log(ESD) - log(EMean) + 1 / (2*(EN - 1)) - (log(CSD) - log(CMean) + 1 / (2*(CN - 1)))
}

Calc.var.lnCVR <- function(CMean, CSD, CN, EMean, ESD, EN, Equal.E.C.Corr=T) {
  if(Equal.E.C.Corr==T){
    mvcorr <- 0 #cor.test(log(c(CMean, EMean)), log(c(CSD, ESD)))$estimate   old, slightly incorrect
    S2 <- CSD^2 / (CN * (CMean^2)) + 1 / (2 * (CN - 1)) - 2 * mvcorr * sqrt((CSD^2 / (CN * (CMean^2))) * (1 / (2 * (CN - 1)))) + ESD^2 / (EN * (EMean^2)) + 1 / (2 * (EN - 1)) - 2 * mvcorr * sqrt((ESD^2 / (EN * (EMean^2))) * (1 / (2 * (EN - 1))))
  }
  else{
    Cmvcorr <- cor.test(log(CMean), log(CSD))$estimate
    Emvcorr <- cor.test(log(EMean), (ESD))$estimate
    S2 <- CSD^2 / (CN * (CMean^2)) + 1 / (2 * (CN - 1)) - 2 * Cmvcorr * sqrt((CSD^2 / (CN * (CMean^2))) * (1 / (2 * (CN - 1)))) + ESD^2 / (EN * (EMean^2)) + 1 / (2 * (EN - 1)) - 2 * Emvcorr * sqrt((ESD^2 / (EN * (EMean^2))) * (1 / (2 * (EN - 1))))		
  }
  S2
}

Calc.lnVR <- function(CSD, CN, ESD, EN){
  log(ESD) - log(CSD) + 1 / (2*(EN - 1)) - 1 / (2*(CN - 1))
}

Calc.var.lnVR <- function( CN,  EN) {
  1 / (2*(EN - 1)) + 1 / (2*(CN - 1))
}

@@

Calc.var.lnRR <- function(CMean, CSD, CN, EMean, ESD, EN) {
  CSD^2/(CN * CMean^2) + ESD^2/(EN * EMean^2)
}

@@

    # Fileter to IMPC source (recommened by Jeremey in email to Susi on 20 Aug 2018)
    filter(datasource_name == 'IMPC') %>%

    # standardise trait names
    mutate(parameter_name = tolower(parameter_name) ) %>%

@@

    # subset to reasonable set of variables
    # date_of_experiment: Jeremy suggested using as an indicator of batch-level effects
    select(production_center, strain_name, strain_accession_id, biological_sample_id, pipeline_stable_id, procedure_group, procedure_name, sex, date_of_experiment, age_in_days, weight, parameter_name, data_point) %>% 
    arrange(production_center, biological_sample_id, age_in_days)
}
```
2) Subsetting the data to choose only one data point per individual per trait
```{r}
#2) Subsetting the data to choose only one data point per individual per trait

# this is a necessary step for the loop across all traits 
data_subset_parameterid_individual_by_age <- function(mydata, parameter, age_min, age_center) {
  tmp <- mydata %>%
    filter(age_in_days >= age_min,
           id == parameter) %>%
    # take results for single individual closest to age_center
    mutate(age_diff = abs(age_center - age_in_days)) %>%
    group_by(biological_sample_id) %>%
    filter(age_diff == min(age_diff)) %>%
    select(-age_diff)

@@

```{r}
## Load raw data - save cleaned dataset as RDS for reuse
#data_raw <- load_raw("data/dr7.0_all_control_data.csv") %>%
#    clean_raw_data()
#dir.create("export", F, F)
#saveRDS(data_raw, "export/data_clean.rds")
getwd()
data1 <- readRDS("export/data_clean.rds") 
#data1 
```

@@

data2 <- dat_moreThan1center
#min(data2$center_per_trait)  # as a check if there indeed are no single occurences

## Meta analysis, Phase 1: across all traits
### Preparation
####Define population variable 
& add grouping variables

@@

 group <- read.csv("export/ParameterGrouping.csv") 
 data <- data3
 data$parameterGroup <- group$parameter[match(data$parameter_name, group$parameter_name)] 
```

@@

```{r}
#head(data)

@@

data <- transform(data, id = match(parameter_name, unique(parameter_name)))
n1 <- length(unique(data$parameter_name)) #232
n2 <- length(unique(data$parameter_group)) #161
n3 <- length(unique(data$procedure_name)) # 26

n <- length(unique(data$id))
#n  # just to check that the number of traits is 232
```

@@

```{r}
results.alltraits.grouping <- as.data.frame(cbind(c(1:n), matrix(rep(0, n*14), ncol = 14))) #number of individual results per trait = 10
names(results.alltraits.grouping) <- c("id", "lnCVR", "lnCVR_lower", "lnCVR_upper", "lnCVR_se", "lnVR", "lnVR_lower", "lnVR_upper", "lnVR_se", "lnRR", "lnRR_lower", "lnRR_upper" ,"lnRR_se" , "sampleSize", "trait")
```

@@

for(t in 1:n) {

  tryCatch({

    data_par_age <- data_subset_parameterid_individual_by_age(data, t, age_min = 0, age_center = 100)

@@

#lnCVR,  log repsonse-ratio of the coefficient of variance    
    cvr <- metafor::rma.mv(yi = effect_size_CVR, V = sample_variance_CVR, random = list(~1| strain_name, ~1|production_center, ~1|err), control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 1000),  verbose=F, data = results)

@@

    #lnVR, comparison of standard deviations

cv <- metafor::rma.mv(yi = effect_size_VR, V = sample_variance_VR, random = list(~1| strain_name, ~1|production_center,~1|err), control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 1000),  verbose=F, data = results)

@@

means <- metafor::rma.mv(yi = effect_size_RR, V = sample_variance_RR, random = list(~1| strain_name, ~1|production_center, ~1|err), control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 1000), data = results)
    results.alltraits.grouping[t, 10] <- means$b
    results.alltraits.grouping[t, 11] <- means$ci.lb
    results.alltraits.grouping[t, 12] <- means$ci.ub
    results.alltraits.grouping[t, 13] <- means$se

        results.alltraits.grouping[t, 14] <- means$k
        results.alltraits.grouping[t, 15] <- unique(results$trait)

  }, error=function(e){cat("ERROR :",conditionMessage(e), "\n")})
}

@@

## Note Susi 31/7/2019: This dataset contains dublicated values, plus no info on what the "traits" mean. I will change Dan N's to one further belwo, that have been cleaned up already
#FILE TO USE: METACOMBO (around line 500)

#trait_meta_results <- write.csv(results.alltraits.grouping, file = "export/trait_meta_results.csv")

@@

```{r}
procedures <- read.csv("export/procedures.csv")

@@

```{r}
meta_clean <- meta1[ !(meta1$id %in% c(84,144,158,160,161,162,163,165,166,167,168,221,222,231)), ]
removed <-length(unique(meta_clean$parameter_name)) #218

meta_problem <- results.alltraits.grouping[ (results.alltraits.grouping$id %in% c(84,144,158,160,161,162,163,165,166,167,168,221,222,231)), ]
```

@@

meta1 <- meta_clean 
# length(unique(meta1$procedure)) #18
# length(unique(meta1$GroupingTerm)) #9 
# length(unique(meta1$parameter_group)) # 148 levels. To be used as grouping factor for meta-meta analysis / collapsing down based on things that are classified identically in "parameter_group" but have different "parameter_name" 
#length(unique(meta1$parameter_name)) #218

@@

kable(cbind (meta1 %>%  count(parameter_group) )) %>%
  kable_styling() %>%
  scroll_box(width = "100%", height = "200px")

meta1b <-
  meta1 %>%
  group_by(parameter_group) %>% 
  summarize(par_group_size = length(unique(parameter_name, na.rm = TRUE)))
#this gives a summary of number of parameter names in each parameter group, now it neeeds to get merged it back together

@@

meta1_sub<-subset(meta1,par_group_size >1) # 90 observations   
meta1_sub$sampleSize <- as.numeric(meta1_sub$sampleSize)

@@

```{r}
# nesting
n_count <- meta1_sub %>% 
  group_by(parameter_group) %>% 
  mutate(raw_N = sum(sampleSize)) %>%  
    nest()

model_count <- n_count %>% 
  mutate(model_lnRR = map(data, ~ robu(.x$lnRR ~ 1, data= .x, studynum= .x$id, modelweights = c("CORR"), rho = 0.8, small = TRUE, var.eff.size= (.x$lnRR_se)^2 )),
  model_lnVR = map(data, ~ robu(.x$lnVR ~ 1, data= .x, studynum= .x$id, modelweights = c("CORR"), rho = 0.8, small = TRUE, var.eff.size= (.x$lnVR_se)^2 )),
  model_lnCVR = map(data, ~ robu(.x$lnCVR ~ 1, data= .x, studynum= .x$id, modelweights = c("CORR"), rho = 0.8, small = TRUE, var.eff.size= (.x$lnCVR_se)^2 ))) 
```

Extract and save parameter estimates:
Function to collect the outcomes of the "mini" meta analysis
```{r}
count_fun <- function(mod_sub)
  return(c(mod_sub$reg_table$b.r, mod_sub$reg_table$CI.L, mod_sub$reg_table$CI.U, mod_sub$reg_table$SE))   #estimate, lower ci, upper ci, SE
```

Extraction of values created during Meta analysis using robu meta:
```{r}
robusub_RR <- model_count %>% 
  transmute(parameter_group, estimatelnRR = map(model_lnRR, count_fun)) %>% 
  mutate(r = map(estimatelnRR, ~ data.frame(t(.)))) %>%
  unnest(r) %>%
  select(-estimatelnRR) %>%
  purrr::set_names(c("parameter_group","lnRR","lnRR_lower","lnRR_upper","lnRR_se"))

robusub_CVR <- model_count %>% 
  transmute(parameter_group, estimatelnCVR = map(model_lnCVR, count_fun)) %>% 
  mutate(r = map(estimatelnCVR, ~ data.frame(t(.)))) %>%
  unnest(r) %>%
  select(-estimatelnCVR) %>%
  purrr::set_names(c("parameter_group","lnCVR","lnCVR_lower","lnCVR_upper","lnCVR_se"))

robusub_VR <- model_count %>% 
  transmute(parameter_group, estimatelnVR = map(model_lnVR, count_fun)) %>% 
  mutate(r = map(estimatelnVR, ~ data.frame(t(.)))) %>%
  unnest(r) %>%
  select(-estimatelnVR) %>%
  purrr::set_names(c("parameter_group","lnVR","lnVR_lower","lnVR_upper","lnVR_se"))

robu_all <- full_join(robusub_CVR, robusub_VR) %>% full_join(., robusub_RR)
kable(cbind(robu_all, robu_all)) %>%
  kable_styling() %>%
  scroll_box(width = "100%", height = "200px")

 Merge the two data sets (the new [robu_all] and the initial [uncorrelated sub-traits with count = 1]) 
```{r}
meta_all <- meta1 %>% filter(par_group_size == 1) %>% as_tibble
#str(meta_all)
#str(robu_all)
#which(is.na(match(names(meta_all),names(robu_all))))  # check
```

#### Combine data 
```{r}
# Step1 
combinedmeta <- bind_rows(robu_all, meta_all)
#glimpse(combinedmeta)

# Steps 2&3
metacombo <- combinedmeta
metacombo$counts <- meta1$par_group_size[match( metacombo$parameter_group, meta1$parameter_group)]
metacombo$procedure2 <-meta1$procedure[match( metacombo$parameter_group, meta1$parameter_group)]
metacombo$GroupingTerm2 <-meta1$GroupingTerm[match( metacombo$parameter_group, meta1$parameter_group)]

kable(cbind (metacombo, metacombo)) %>%
  kable_styling() %>%
  scroll_box(width = "100%", height = "200px")

 Clean-up and rename 
```{r}
metacombo <-metacombo[, c(1, 21:23, 2:13)] 
names(metacombo)[3] <- "procedure" 
names(metacombo)[4] <- "GroupingTerm"

@@

compare <- metacombo %>%
  group_by(GroupingTerm) %>%
  dplyr::summarize(MeanCVR = mean(lnCVR),MeanVR = mean(lnVR), MeanRR = mean(lnRR) )

compare

@@

## Note Susi 31/7/2019: This has been cleaned up already
#FILE TO USE: METACOMBO 
  ### note: to use

#trait_meta_results <- write.csv(metacombo, file = "export/trait_meta_results.csv")
```

@@

kable(cbind (metacombo,metacombo)) %>%
  kable_styling() %>%
  scroll_box(width = "100%", height = "200px")

@@

  mutate(model_lnCVR = map(data, ~ metafor::rma.uni(yi = .x$lnCVR, sei = (.x$lnCVR_upper - .x$lnCVR_lower)/ (2*1.96),  
				control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 1000), verbose=F)),
	   model_lnVR = map(data, ~ metafor::rma.uni(yi = .x$lnVR, sei = (.x$lnVR_upper - .x$lnVR_lower)/ (2*1.96),  
				control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 1000), verbose=F)),
	   model_lnRR = map(data, ~ metafor::rma.uni(yi = .x$lnRR, sei = (.x$lnRR_upper - .x$lnRR_lower)/ (2*1.96),  
				control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 1000), verbose=F)))

@@

  mutate(model_lnCVR = map(data, ~ metafor::rma.uni(yi = .x$lnCVR, sei = (.x$lnCVR_upper - .x$lnCVR_lower)/ (2*1.96),  
				control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 1000), verbose=F)),
	   model_lnVR = map(data, ~ metafor::rma.uni(yi = .x$lnVR, sei = (.x$lnVR_upper - .x$lnVR_lower)/ (2*1.96),  
				control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 1000), verbose=F)),
	   model_lnRR = map(data, ~ metafor::rma.uni(yi = .x$lnRR, sei = (.x$lnRR_upper - .x$lnRR_lower)/ (2*1.96),  
				control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 1000), verbose=F)))

@@

```{r}
Behaviour <- as.data.frame(overall1 %>% filter(., GroupingTerm == "Behaviour")    %>%  mutate(lnCVR=.[[4]][[1]]$b, lnCVR_lower=.[[4]][[1]]$ci.lb, lnCVR_upper=.[[4]][[1]]$ci.ub, lnCVR_se=.[[4]][[1]]$se,
	              lnVR=.[[5]][[1]]$b, lnVR_lower=.[[5]][[1]]$ci.lb, lnVR_upper=.[[5]][[1]]$ci.ub, lnVR_se=.[[5]][[1]]$se,
		        lnRR=.[[6]][[1]]$b, lnRR_lower=.[[6]][[1]]$ci.lb, lnRR_upper=.[[6]][[1]]$ci.ub, lnRR_se=.[[6]][[1]]$se) )[, c(1,7:18)]

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  warning = FALSE,
  message = FALSE,
  cache = TRUE,
  tidy = TRUE
)

@@

@@

```{r}
library(readr)
library(dplyr)
library(metafor)
library(devtools)
library(purrr)
library(tidyverse)
library(tibble)
library(kableExtra)
library(robumeta)
library(ggpubr)
library(ggplot2)
library(here)
```

### Loading functions 
#### Functions for preparing the data for meta analyses
1) "Population statistics"
```{r}
calculate_population_stats <- function(mydata, min_individuals = 5) {
  mydata %>%
    group_by(population, strain_name, production_center, sex) %>%
    summarise(
      trait = parameter_name[1],
      x_bar = mean(data_point),
      x_sd = sd(data_point),
      n_ind = n()
    ) %>%
    ungroup() %>%
    filter(n_ind > min_individuals) %>%
    # Check both sexes present & filter those missing
    group_by(population) %>%
    mutate(
      n_sex = n_distinct(sex)
    ) %>%
    ungroup() %>%
    filter(n_sex == 2) %>%
    select(-n_sex) %>%
    arrange(production_center, strain_name, population, sex)
}
```

@@

  mydata[i, ] %>%
    select(strain_name, production_center, trait) %>%
    mutate(
      effect_size_CVR = Calc.lnCVR(CMean = input$x1i, CSD = input$sd1i, CN = input$n1i, EMean = input$x2i, ESD = input$sd2i, EN = input$n2i),
      sample_variance_CVR = Calc.var.lnCVR(CMean = input$x1i, CSD = input$sd1i, CN = input$n1i, EMean = input$x2i, ESD = input$sd2i, EN = input$n2i),
      effect_size_VR = Calc.lnVR(CSD = input$sd1i, CN = input$n1i, ESD = input$sd2i, EN = input$n2i),
      sample_variance_VR = Calc.var.lnVR(CN = input$n1i, EN = input$n2i),
      effect_size_RR = Calc.lnRR(CMean = input$x1i, CSD = input$sd1i, CN = input$n1i, EMean = input$x2i, ESD = input$sd2i, EN = input$n2i),
      sample_variance_RR = Calc.var.lnRR(CMean = input$x1i, CSD = input$sd1i, CN = input$n1i, EMean = input$x2i, ESD = input$sd2i, EN = input$n2i),
      err = as.factor(seq_len(n()))
    )
}
```

@@

Calc.lnCVR <- function(CMean, CSD, CN, EMean, ESD, EN) {
  log(ESD) - log(EMean) + 1 / (2 * (EN - 1)) - (log(CSD) - log(CMean) + 1 / (2 * (CN - 1)))
}

Calc.var.lnCVR <- function(CMean, CSD, CN, EMean, ESD, EN, Equal.E.C.Corr = T) {
  if (Equal.E.C.Corr == T) {
    mvcorr <- 0 # cor.test(log(c(CMean, EMean)), log(c(CSD, ESD)))$estimate   old, slightly incorrect
    S2 <- CSD^2 / (CN * (CMean^2)) + 1 / (2 * (CN - 1)) - 2 * mvcorr * sqrt((CSD^2 / (CN * (CMean^2))) * (1 / (2 * (CN - 1)))) + ESD^2 / (EN * (EMean^2)) + 1 / (2 * (EN - 1)) - 2 * mvcorr * sqrt((ESD^2 / (EN * (EMean^2))) * (1 / (2 * (EN - 1))))
  }
  else {
    Cmvcorr <- cor.test(log(CMean), log(CSD))$estimate
    Emvcorr <- cor.test(log(EMean), (ESD))$estimate
    S2 <- CSD^2 / (CN * (CMean^2)) + 1 / (2 * (CN - 1)) - 2 * Cmvcorr * sqrt((CSD^2 / (CN * (CMean^2))) * (1 / (2 * (CN - 1)))) + ESD^2 / (EN * (EMean^2)) + 1 / (2 * (EN - 1)) - 2 * Emvcorr * sqrt((ESD^2 / (EN * (EMean^2))) * (1 / (2 * (EN - 1))))
  }
  S2
}

Calc.lnVR <- function(CSD, CN, ESD, EN) {
  log(ESD) - log(CSD) + 1 / (2 * (EN - 1)) - 1 / (2 * (CN - 1))
}

Calc.var.lnVR <- function(CN, EN) {
  1 / (2 * (EN - 1)) + 1 / (2 * (CN - 1))
}

@@

Calc.var.lnRR <- function(CMean, CSD, CN, EMean, ESD, EN) {
  CSD^2 / (CN * CMean^2) + ESD^2 / (EN * EMean^2)
}
```

@@

    # Fileter to IMPC source (recommened by Jeremey in email to Susi on 20 Aug 2018)
    filter(datasource_name == "IMPC") %>%

    # standardise trait names
    mutate(parameter_name = tolower(parameter_name)) %>%

@@

    # subset to reasonable set of variables
    # date_of_experiment: Jeremy suggested using as an indicator of batch-level effects
    select(production_center, strain_name, strain_accession_id, biological_sample_id, pipeline_stable_id, procedure_group, procedure_name, sex, date_of_experiment, age_in_days, weight, parameter_name, data_point) %>%
    arrange(production_center, biological_sample_id, age_in_days)
}
```
2) Subsetting the data to choose only one data point per individual per trait
```{r}
# 2) Subsetting the data to choose only one data point per individual per trait

# this is a necessary step for the loop across all traits
data_subset_parameterid_individual_by_age <- function(mydata, parameter, age_min, age_center) {
  tmp <- mydata %>%
    filter(
      age_in_days >= age_min,
      id == parameter
    ) %>%
    # take results for single individual closest to age_center
    mutate(age_diff = abs(age_center - age_in_days)) %>%
    group_by(biological_sample_id) %>%
    filter(age_diff == min(age_diff)) %>%
    select(-age_diff)

@@

```{r}
## Load raw data - save cleaned dataset as RDS for reuse
# data_raw <- load_raw("data/dr7.0_all_control_data.csv") %>%
#    clean_raw_data()
# dir.create("export", F, F)
# saveRDS(data_raw, "export/data_clean.rds")
# getwd()
data1 <- readRDS(here("export", "data_clean.rds"))
# data1
```

@@

data2 <- dat_moreThan1center
# min(data2$center_per_trait)  # as a check if there indeed are no single occurences
```

## Meta analysis, Phase 1: across all traits
### Preparation
#### Define population variable 
& add grouping variables

@@

group <- read.csv(here("export", "ParameterGrouping.csv"))
data <- data3
data$parameterGroup <- group$parameter[match(data$parameter_name, group$parameter_name)]
```

@@

```{r}
# head(data)

@@

data <- transform(data, id = match(parameter_name, unique(parameter_name)))
n1 <- length(unique(data$parameter_name)) # 232
n2 <- length(unique(data$parameter_group)) # 161
n3 <- length(unique(data$procedure_name)) # 26

n <- length(unique(data$id))
# n  # just to check that the number of traits is 232
```

@@

```{r}
results.alltraits.grouping <- as.data.frame(cbind(c(1:n), matrix(rep(0, n * 14), ncol = 14))) # number of individual results per trait = 10
names(results.alltraits.grouping) <- c("id", "lnCVR", "lnCVR_lower", "lnCVR_upper", "lnCVR_se", "lnVR", "lnVR_lower", "lnVR_upper", "lnVR_se", "lnRR", "lnRR_lower", "lnRR_upper", "lnRR_se", "sampleSize", "trait")
```

@@

for (t in 1:n) {
  tryCatch(
    {
      data_par_age <- data_subset_parameterid_individual_by_age(data, t, age_min = 0, age_center = 100)

@@

      # lnCVR,  log repsonse-ratio of the coefficient of variance
      cvr <- metafor::rma.mv(yi = effect_size_CVR, V = sample_variance_CVR, 
                             random = list(~ 1 | strain_name, ~ 1 | production_center, ~ 1 | err), control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F, data = results)

@@

      # lnVR, comparison of standard deviations

      cv <- metafor::rma.mv(yi = effect_size_VR, V = sample_variance_VR, random = list(~ 1 | strain_name, ~ 1 | production_center, ~ 1 | err), control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F, data = results)

@@

      means <- metafor::rma.mv(yi = effect_size_RR, V = sample_variance_RR, random = list(~ 1 | strain_name, ~ 1 | production_center, ~ 1 | err), control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), data = results)
      results.alltraits.grouping[t, 10] <- means$b
      results.alltraits.grouping[t, 11] <- means$ci.lb
      results.alltraits.grouping[t, 12] <- means$ci.ub
      results.alltraits.grouping[t, 13] <- means$se

      results.alltraits.grouping[t, 14] <- means$k
      results.alltraits.grouping[t, 15] <- unique(results$trait)
    },
    error = function(e) {
      cat("ERROR :", conditionMessage(e), "\n")
    }
  )
}

@@

## Note Susi 31/7/2019: This dataset contains dublicated values, plus no info on what the "traits" mean. I will change Dan N's to one further belwo, that have been cleaned up already
# FILE TO USE: METACOMBO (around line 500)

# trait_meta_results <- write.csv(results.alltraits.grouping, file = "export/trait_meta_results.csv")
```

@@

```{r}
procedures <- read.csv(here("export", "procedures.csv"))

@@

```{r}
meta_clean <- meta1[ !(meta1$id %in% c(84, 144, 158, 160, 161, 162, 163, 165, 166, 167, 168, 221, 222, 231)), ]
removed <- length(unique(meta_clean$parameter_name)) # 218

meta_problem <- results.alltraits.grouping[ (results.alltraits.grouping$id %in% c(84, 144, 158, 160, 161, 162, 163, 165, 166, 167, 168, 221, 222, 231)), ]
```

@@

meta1 <- meta_clean
# length(unique(meta1$procedure)) #18
# length(unique(meta1$GroupingTerm)) #9
# length(unique(meta1$parameter_group)) # 148 levels. To be used as grouping factor for meta-meta analysis / collapsing down based on things that are classified identically in "parameter_group" but have different "parameter_name"
# length(unique(meta1$parameter_name)) #218
```

@@

kable(cbind(meta1 %>% count(parameter_group))) %>%
  kable_styling() %>%
  scroll_box(width = "100%", height = "200px")

meta1b <-
  meta1 %>%
  group_by(parameter_group) %>%
  summarize(par_group_size = length(unique(parameter_name, na.rm = TRUE)))
# this gives a summary of number of parameter names in each parameter group, now it neeeds to get merged it back together

@@

meta1_sub <- subset(meta1, par_group_size > 1) # 90 observations
meta1_sub$sampleSize <- as.numeric(meta1_sub$sampleSize)
```

@@

```{r}
# nesting
n_count <- meta1_sub %>%
  group_by(parameter_group) %>%
  mutate(raw_N = sum(sampleSize)) %>%
  nest() %>%
  ungroup()

model_count <- n_count %>%
  mutate(
    model_lnRR = map(data, ~ robu(.x$lnRR ~ 1, data = .x, studynum = .x$id, modelweights = c("CORR"), rho = 0.8, small = TRUE, var.eff.size = (.x$lnRR_se)^2)),
    model_lnVR = map(data, ~ robu(.x$lnVR ~ 1, data = .x, studynum = .x$id, modelweights = c("CORR"), rho = 0.8, small = TRUE, var.eff.size = (.x$lnVR_se)^2)),
    model_lnCVR = map(data, ~ robu(.x$lnCVR ~ 1, data = .x, studynum = .x$id, modelweights = c("CORR"), rho = 0.8, small = TRUE, var.eff.size = (.x$lnCVR_se)^2))
  )
```

Extract and save parameter estimates:
Function to collect the outcomes of the "mini" meta analysis
```{r}
count_fun <- function(mod_sub) {
  return(c(mod_sub$reg_table$b.r, mod_sub$reg_table$CI.L, mod_sub$reg_table$CI.U, mod_sub$reg_table$SE))
} # estimate, lower ci, upper ci, SE
```

Extraction of values created during Meta analysis using robu meta:
```{r}
robusub_RR <- model_count %>%
  transmute(parameter_group, estimatelnRR = map(model_lnRR, count_fun)) %>%
  mutate(r = map(estimatelnRR, ~ data.frame(t(.)))) %>%
  unnest(r) %>%
  select(-estimatelnRR) %>%
  purrr::set_names(c("parameter_group", "lnRR", "lnRR_lower", "lnRR_upper", "lnRR_se"))

robusub_CVR <- model_count %>%
  transmute(parameter_group, estimatelnCVR = map(model_lnCVR, count_fun)) %>%
  mutate(r = map(estimatelnCVR, ~ data.frame(t(.)))) %>%
  unnest(r) %>%
  select(-estimatelnCVR) %>%
  purrr::set_names(c("parameter_group", "lnCVR", "lnCVR_lower", "lnCVR_upper", "lnCVR_se"))

robusub_VR <- model_count %>%
  transmute(parameter_group, estimatelnVR = map(model_lnVR, count_fun)) %>%
  mutate(r = map(estimatelnVR, ~ data.frame(t(.)))) %>%
  unnest(r) %>%
  select(-estimatelnVR) %>%
  purrr::set_names(c("parameter_group", "lnVR", "lnVR_lower", "lnVR_upper", "lnVR_se"))

robu_all <- full_join(robusub_CVR, robusub_VR) %>% full_join(., robusub_RR)
```

```{r}
kable(cbind(robu_all, robu_all)) %>%
  kable_styling() %>%
  scroll_box(width = "100%", height = "200px")
```

 Merge the two data sets (the new [robu_all] and the initial [uncorrelated sub-traits with count = 1]) 
```{r}
meta_all <- meta1 %>%
  filter(par_group_size == 1) %>%
  as_tibble()
# str(meta_all)
# str(robu_all)
# which(is.na(match(names(meta_all),names(robu_all))))  # check
```

#### Combine data 
```{r}
# Step1
combinedmeta <- bind_rows(robu_all, meta_all)
# glimpse(combinedmeta)

# Steps 2&3
metacombo <- combinedmeta
metacombo$counts <- meta1$par_group_size[match(metacombo$parameter_group, meta1$parameter_group)]
metacombo$procedure2 <- meta1$procedure[match(metacombo$parameter_group, meta1$parameter_group)]
metacombo$GroupingTerm2 <- meta1$GroupingTerm[match(metacombo$parameter_group, meta1$parameter_group)]

kable(cbind(metacombo, metacombo)) %>%
  kable_styling() %>%
  scroll_box(width = "100%", height = "200px")
```

 Clean-up and rename 
```{r}
metacombo <- metacombo[, c(1, 21:23, 2:13)]
names(metacombo)[3] <- "procedure"
names(metacombo)[4] <- "GroupingTerm"

@@

compare <- metacombo %>%
  group_by(GroupingTerm) %>%
  dplyr::summarize(MeanCVR = mean(lnCVR), MeanVR = mean(lnVR), MeanRR = mean(lnRR))

# compare
```

@@

## Note Susi 31/7/2019: This has been cleaned up already
# FILE TO USE: METACOMBO
### note: to use

# trait_meta_results <- write.csv(metacombo, file = "export/trait_meta_results.csv")
```

@@

kable(cbind(metacombo, metacombo)) %>%
  kable_styling() %>%
  scroll_box(width = "100%", height = "200px")
```

@@

  mutate(
    model_lnCVR = map(data, ~ metafor::rma.uni(
      yi = .x$lnCVR, sei = (.x$lnCVR_upper - .x$lnCVR_lower) / (2 * 1.96),
      control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
    )),
    model_lnVR = map(data, ~ metafor::rma.uni(
      yi = .x$lnVR, sei = (.x$lnVR_upper - .x$lnVR_lower) / (2 * 1.96),
      control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
    )),
    model_lnRR = map(data, ~ metafor::rma.uni(
      yi = .x$lnRR, sei = (.x$lnRR_upper - .x$lnRR_lower) / (2 * 1.96),
      control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
    ))
  )

@@

  mutate(
    model_lnCVR = map(data, ~ metafor::rma.uni(
      yi = .x$lnCVR, sei = (.x$lnCVR_upper - .x$lnCVR_lower) / (2 * 1.96),
      control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
    )),
    model_lnVR = map(data, ~ metafor::rma.uni(
      yi = .x$lnVR, sei = (.x$lnVR_upper - .x$lnVR_lower) / (2 * 1.96),
      control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
    )),
    model_lnRR = map(data, ~ metafor::rma.uni(
      yi = .x$lnRR, sei = (.x$lnRR_upper - .x$lnRR_lower) / (2 * 1.96),
      control = list(optimizer = "optim", optmethod = "Nelder-Mead", maxit = 1000), verbose = F
    ))
  )
```

@@

```{r}
Behaviour <- as.data.frame(overall1 %>% filter(., GroupingTerm == "Behaviour") %>% mutate(
  lnCVR = .[[4]][[1]]$b, lnCVR_lower = .[[4]][[1]]$ci.lb, lnCVR_upper = .[[4]][[1]]$ci.ub, lnCVR_se = .[[4]][[1]]$se,
  lnVR = .[[5]][[1]]$b, lnVR_lower = .[[5]][[1]]$ci.lb, lnVR_upper = .[[5]][[1]]$ci.ub, lnVR_se = .[[5]][[1]]$se,
  lnRR = .[[6]][[1]]$b, lnRR_lower = .[[6]][[1]]$ci.lb, lnRR_upper = .[[6]][[1]]$ci.ub, lnRR_se = .[[6]][[1]]$se
))[, c(1, 7:18)]
